### 2017-07-04 readme.Rmd
update readme

Now let's plot these models.
```{r,fig.width=12,fig.height=6, eval=FALSE}
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_warton_cell,col=jet.colors(100))
```

>>>>

Now let's plot these models.
```{r,fig.width=8,fig.height=6}
jet.colors <- colorRampPalette(rev(RColorBrewer::brewer.pal(11 , "Spectral")))
plot(p_warton_cell,col=jet.colors(100))
```
